Figures for Paper

### 2021-07-21 paper_figures.Rmd

cowplot::plot_grid(rap1_fold_plot,pfkp_fold_plot)

>>>>

cowplot::plot_grid(rap1_fold_plot,pfkp_fold_plot)
```
# Nanopore

Read in pre-processed data (see separate script) and plot
```{r warning=FALSE, message=FALSE}
df <- read_csv(paste0(here(),
                      "/data/nanopore/combined_nanopore_dataframe.csv"))

df[is.na(df)] <- 0

p2_patient <- ggplot(df %>% filter(classification != "Neither",
                                   type=="Patient"), aes(x = name, y = 100*fraction, fill = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("Patient RNA") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

p2_shsy <- ggplot(df %>% filter(classification != "Neither",
                                type=="SHSY5Y"), aes(x = name, y = 100*fraction, fill = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("SH-SY5Y") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

p2_shsy | p2_patient

# without neither removed

p2_patient <- ggplot(df %>% filter(classification != "",
                                   type=="Patient"), aes(x = name, y = 100*fraction, fill = class2,
                                                         colour = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("Patient RNA") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

p2_shsy <- ggplot(df %>% filter(classification != "",
                                type=="SHSY5Y"), aes(x = name, y = 100*fraction, fill = class2,
                                                     colour = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("SH-SY5Y") +
    xlab("") +
    ggeasy::easy_add_legend_title("") 
p2_shsy | p2_patient

# fractional

df2 <- df %>%
    filter(classification != "Neither") %>%
    group_by(name) %>%
    mutate(f = n/sum(n))

ggplot(df2, aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

ggplot(df2 %>%
           filter(type == "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("") |
    ggplot(df2 %>%
           filter(type != "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("")
